---
editor_options:
  chunk_output_type: console
---

## Mis-Specification Analyis (MSA)

> To trust inferences drawn from econometric analyses, one must check that the underlying assumptions are satisfied. [@hendry2007econometric]

- [tag: diagnostic, CrossValidated](https://stats.stackexchange.com/questions/tagged/diagnostic) Diagnostic measures (such as residuals or some summary statistics calculated from residuals) are used to evaluate some aspect of quality of model fit to data.

### Normality

#### (a) Analyse Residuals Graphically {-}

- [Interpreting plot.lm(), CrossValidated](https://stats.stackexchange.com/a/65864/231405)
- section 1.5.1 model fitting and model checking in [@wood2017generalized].
- [Regression diagnostic plots](http://strata.uga.edu/8370/rtips/regressionPlots.html), Data Analysis in the Geosciences, Steven Holland

For example, the following four plots can be used to check the plausibility of normality assumptions:

```{r, warning=FALSE}
par_orginal <- par()
par(mfrow = c(2, 2), mai = c(0.3, 0.3, 0.3, 0.3))
plot(mods_recs[[6]])
par(par_orginal)
```

- The upper left plot shows residuals against fitted values of `mods_recs[[1]]`. It is hard to trust indication the flat trending line because there are few data points with low fitted values. The variance seems to be stable when fitted values are high. The assumption of homoskedasticity is tested formally in section 4.
- Data points `36`, `241` and `163` are mentioned in all but the lower right plots. They are examined in section 6.
- The assumption of conditional normality looks reasonable according to the upper right Q-Q plot. A formal Jarque-Bera test is performed later this section to examine this assumption in a quantitative manner.

#### (b) Jarque-Bera Test (test-JB) {-}

The assumption of conditional normality is justified by JB test.

```{r, echo=T}
mods_recs[[1]] %>% test_jb(dat_recs) %>% tab_ti()
```

#### (c) Address the Normality Problem {-}

- Look at the data.
- Change the distributional assumption.
- Check the robustness of the method.

### Homoskedasticity

#### White's Test (test-White) {-}

- [Econometrics : White Test with R, CrossValidated](https://stackoverflow.com/a/61040739/10181743)

`mods_recs[[1]]` cannot pass the White's test, which means the variances of residuals do vary with different values of `y`.

```{r, echo=T}
mods_recs[[1]] %>% test_white(dat_recs, resi2 ~ x2 + I(x2^2), 2) %>% tab_ti()
```

### Functional Form

#### RESET Test (test-RESET) {-}

`mods_recs[[1]]` can pass RESET test.

```{r, echo=T, warning=F, message=F}
mods_recs[[1]] %>% test_reset(dat_recs) %>% tab_ti()
```

- [Does lm() use partial correlation - R Squared Change, CrossValidated](https://stats.stackexchange.com/questions/37785/does-lm-use-partial-correlation-r-squared-change)
