
## Orthogonalization

### Regress `y` on `x2`, Assumptions and Orthogonalization

`mods[[1]]` is obtained by regressing `y` on `x2`.

```{r}
mods <- list()
mods[[1]] <- lm(y ~ x2, data = dat)

mods[[1]] -> model  # Print model summary
model$call
model %>% tidy() %>% tab_ti(F)
model %>% glance() %>% tab_ti(F)
rm(model)

results <- new_results(mods[[1]], 1)
```

By orthogonalizing `x2` with respect to constant 1. the following reparameterized model can be obtained.

```{r, echo=T}
mods[[2]] <- 
  dat %>%
  mutate(x1 = 1, x21 = x2 - mean(.$x2)) %>%
  dplyr::select(y, x1, x21) %>%
  {lm(y ~ x1 + x21, data = .)}
```

```{r}
results %<>%
  collect_glance(mods[[2]], 2)

mods[[2]] -> model  # Print model summary
model$call
model %>% tidy() %>% tab_ti(F)
model %>% glance() %>% tab_ti(F)
rm(model)
```

The estimated regression coefficient for `x2` in `mods[[1]]` equals that for `x21` in `mods[[2]]`. That is, slopes in these two models are the same. The standard error of the intercept is reduced by 51.60 %.
