---
editor_options:
  chunk_output_type: console
---

## Visualization

The first 5 rows of the dat_recsa set used can be visualized:

```{r}
head(dat_recs, 5) %>% tab_ti(F)
```

### Covariance Matrix

```{r}
dat_recs %>%
  cor() %>%
  as_cordf() %>%
  stretch() %>%
  dplyr::filter(y == "y" & x != "y") %>%
  tab_ti(F)
```

### Box Plot

For each level of `x2` a box indicating three quantiles (25%, 50%, 75%) of `y` is given. It shows that there is a tendency for `y` to decrease with `x2` by looking at the median. The sizes of different boxes seem to vary with different values of `x2`. Besides, there are many observations when `x2` is small. But it is assumed for now that the conditional variance is constant, which will be tested section 4. Three dat_recsa points with extreme values `36`, `241` and `163` is discussed in sections 3 and 5.

```{r}
dat_recs %>%
  mutate(index = row_number()) %>%
  ggplot() +
    geom_boxplot(aes(x2, y, group = cut_width(x2, 1)), outlier.alpha = 0) +
    geom_point(aes(x2, y), shape = 1) +
    geom_text(aes(x2, y, label = ifelse(index == 36 | index == 163 |
      index == 241, as.character(index), "")), hjust=1.5, vjust=0)
```

The box plot of `y` by `x6` is given. It can be seen that the tendency is not strictly linear and the condition variance is not stable. So we will regress `y` on `x2` first and use `x6` as the second regressor in section 6.

```{r}
dat_recs %>%
  ggplot() +
  geom_boxplot(aes(x6, y, group = cut_width(x6, 10)), outlier.alpha = 0)+
    geom_point(aes(x6, y), shape = 1)
```
