---
editor_options:
  chunk_output_type: console
---

## Interval Estimation

### Confidence Interval of Parameters

> The width of these confidence intervals is a measure of the overall quality of the regression line. [@montgomery2012introduction]

> By choosing a 95% coverage, we accept that with 5% confidence we reach the false conclusion that the true parameter is not in the confidence interval. -- section 2.3.1 confidence intervals in [@hendry2007econometric]

For example, the confidence interval of `mods_recs[[1]]` can be calculated using `stats::confint()`.

```{r, echo=T}
mods_recs[[1]] %>% stats::confint() %>% as_tibble() %>% tab_ti()
```

### Confidence Interval of Mean Responses

> A major use of a regression model is to estimate the mean response $\mathrm{E}(y)$ for a particular value of the regressor variable $x$. [@montgomery2012introduction]

- [Calculating Prediction Interval, CrossValidated](https://stats.stackexchange.com/questions/69144/calculating-prediction-interval)

```{r, echo=T}
int_conf <-
  mods_census[[1]] %>%
  predict(interval = "confidence", level = .95) %>%
  as_tibble() %>%
  select(lwr.conf = lwr, upr.conf = upr)
```

### Prediction Interval of New Observations

> The CI on the mean response is inappropriate for this problem because it is an interval estimate on the mean of y (a parameter), not a probability statement about future observations from that distribution. [@montgomery2012introduction]

```{r, echo=T}
int_pred <-
  mods_census[[1]] %>%
  predict(newdata = data.frame(educ = dat_census$educ),
    interval = "prediction", level = .95) %>%
  as_tibble() %>%
  select(lwr.pred = lwr, upr.pred = upr)
```

```{r}
dat_census %>%
  bind_cols(int_pred, int_conf) %>%
  ggplot() +
    geom_point(mapping = aes(x = educ, y = wage_log)) +
    geom_line(aes(educ, lwr.conf), color='red') +
    geom_line(aes(educ, upr.conf), color='red') +
    geom_line(aes(educ, lwr.pred), color='blue') +
    geom_line(aes(educ, upr.pred), color='blue')
```

`add_predictions()` can be used to generate predictions.

```{r, echo=T}
dat_census %>%
  add_predictions(mods_census[[1]]) %>%
  head(5) %>%
  tab_ti()
```
