---
editor_options:
  chunk_output_type: console
---

## Statistical Inference

### Hypothesis Tests

> The __null hypothesis__, denoted by $\mathrm{H}_{0}$, is a statement about a population parameter. The __alternative hypothesis__ is denoted by $\mathrm{H}_{1}$. The null hypothesis will be rejected if it appears to be inconsistent with the sample data and will not be rejected otherwise. [@ross2017introductory]

#### (a) Test Statistic and Critical Region {-}

> A __test statistic__ is a statistic whose value is determined from the sample data. Depending on the value of this test statistic, the null hypothesis will be rejected or not. The __critical region__, also called the __rejection region__, is that set of values of the test statistic for which the null hypothesis is rejected. [@ross2017introductory]

> The classical procedure for testing a null hypothesis is to fix a small __level of significance__ $\alpha$ and then require that the probability of rejecting $\mathrm{H}_{0}$ when $\mathrm{H}_{0}$ is true is less than or equal to $\alpha$. [@ross2017introductory]

Critical values are calculated by:

```R
c <- qchisq(1 - alpha, df, lower.tail = TRUE, log.p = FALSE)
```

The hypothesis should be rejected if `stat >= c` is true.

Alternatively, `p_value` can be computed first:

```R
1 - pchisq(stat, df1)
```

and compared to `alpha`. The hypothesis should be rejected if `p_value >= alpha` is true.

#### (b) Design of Hypothesis Tests {-}

> If you are trying to establish a certain hypothesis, then that hypothesis should be designated as the alternative hypothesis. Similarly, if you are trying to discredit a hypothesis, that hypothesis should be designated the null hypothesis. [@ross2017introductory]

```{example, nicotine, name='Nicotine Test', echo=T}
Thus, for instance, if the tobacco company is running the experiment to prove that the mean nicotine level of its cigarettes is less than $1.5,$ then it should choose for the null hypothesis

$$ \mathrm{H}_{0}: \mu \geq 1.5 $$

and for the alternative hypothesis

$$ \mathrm{H}_{1}: \mu<1.5 $$

Then the company could use a rejection of the null hypothesis as "proof" of its claim that the mean nicotine content was less than 1.5 milligrams.
```

#### (c) Interpretation of Test Result {-}

> The rejection of the null hypothesis $\mathrm{H}_{0}$ is a strong statement that $\mathrm{H}_{0}$ does not appear to be consistent with the observed data. The result that $\mathrm{H}_{0}$ is not rejected is a weak statement that should be interpreted to mean that $\mathrm{H}_{0}$ is consistent with the data. [@ross2017introductory]

> When conducting a statistical test, the thought experiment is that our sample is drawn from some hypothetical population distribution that could have generated the data. Our sample is then compared with hypothetical samples drawn from that hypothetical population distribution. -- section 4.3.2, interpreting the test result in [@hendry2007econometric]

### Student's t-Test (test-t) {#test-t}

- [One-Sided Hypothesis Test with T-Statistic in R?, Stack Overflow](https://stackoverflow.com/questions/13811472/one-sided-hypothesis-test-with-t-statistic-in-r)
- [t-tests, Quick-R](https://www.statmethods.net/stats/ttest.html)
- [Inference about Slope coefficient in R](https://stackoverflow.com/questions/8089797/inference-about-slope-coefficient-in-r)

### Log-Likelihood Ratio Test (test-LLR) {#test-LLR}

> Likelihood ratio tests are well suited for making inferences about restrictions on a well-specified model, where we are able, and willing, to maximize the likelihood function in the unrestricted model as well as the restricted model. [@hendry2007econometric]

$$ \mathrm{Q} = \frac{\max _{\theta \in \Theta_{R}} \mathrm{L}_{Y_{1}, \ldots, Y_{n}}(\theta)}{\max _{\theta \in \Theta_{U}} \mathrm{L}_{Y_{1}, \ldots, Y_{n}}(\theta)} $$

$$ \mathrm{LR} = -2 \log \mathrm{Q} = 2 \left\{\max _{\theta \in \Theta_{U}} \ell_{Y_{1}, \ldots, Y_{n}}(\theta)-\max _{\theta \in \Theta_{R}} \ell_{Y_{1}, \ldots, Y_{n}}(\theta)\right\} $$

where the closer $\mathrm{LR}$ is to zero, the more likely it is that $\theta$ could satisfy the restriction.

A statistical test can now be constructed as a decision rule. If $\mathrm{Q}$ is (close to) unity, and correspondingly $\mathrm{LR}$ is small, the restricted maximum likelihood estimate would be (nearly) as likely as the unrestricted estimate, so in that case, we would fail to reject the hypothesis.

#### (a) Signed test-LLR {-#test-LLR-sign}

- [If and how to use one-tailed testing in multiple regression](https://stats.stackexchange.com/questions/325354/if-and-how-to-use-one-tailed-testing-in-multiple-regression)

```{r, echo=T}
test_llr(mods_part[[1]], mods_part[[2]]) %>% tab_ti()
```

This signed likelihood ratio statistic is approximately normally distributed when the hypothesis is true:
$$ \omega=\operatorname{sign}\left(\widehat{\beta} \right) \sqrt{\mathrm{LR}} \stackrel{\mathrm{D}}{\approx} \mathrm{N}[0,1] $$
where the sign function is given by:
$$ \operatorname{sign}(x) = \left\{\begin{array}{ll}
+1 & \text { if } x \geq 0 \\
-1 & \text { if } x<0
\end{array} \right. $$
Then we construct a test by comparing the test statistic $\omega$ to a critical value $c$.

```{r, echo=T}
test_llr_sign(mods_part[[1]], mods_part[[2]], T) %>% tab_ti()
```

#### (b) Analysis of Variance (ANOVA) {-#ANOVA}

When there is only one regressor, the sample correlation is represented by `r.squared`, which is a measure of goodness-of-fit of the unrestricted model relative to the restricted model. [@hendry2007econometric] Take the example \@ref(exm:census) `census` for example:

```{r, echo=T}
mods_census[[1]] %>% glance() %>% tab_ti()
```

The `deviance` is the residual sum of square.

When there are multiple regressors, partial sample correlations can be obtained by the 6th column using `tab_tidy()`.

```{r, message=F, warning=F}
mods_census[[2]] %>% tab_tidy()
```

The log-likelihood ratio test statistic for any parameter being 0 can be calculated using partial sample correlations and the following equation:
$$ \mathrm{LR}=-n \log \left(1-r^{2} \right). $$

```{r, echo=T}
mods_census[[2]] %>%
  tab_tidy(T) %>%
  {.[3, 6]} %>%
  as.numeric() %>%
  {- 3877 * log(1 - .)}
```

or using `test_llr()` to compare two models: (the restricted model is the one with less regressors)

```{r, echo=T}
test_llr(mods_census[[2]], mods_census[[1]]) %>% tab_ti()
```

or using `stats::anova()`:

```{r}
mods_census[[2]] %>% stats::anova() %>% tidy() %>% tab_ti()
```

As for the example \@ref(exm:RECS) `RECS`, to test the hypothesis that coefficient for `x5` is 0 in `mods_recs[[1]]`, `tab_tidy()` is used:

```{r, warning=F, message=F}
mods_recs[[1]] %>% tab_tidy()
```

#### (c) LLR-Test for More Parameters {-#LLR-Test-N}

Likelihood tests for restricting more than one parameter can be only performed by using values of log likelihood in the original and restricted models. For example, to test the hypothesis that coefficients for `x5` and `x7` are both 0 in `mods_recs[[1]]`, following calculation can be conducted. We cannot reject the hypothesis according the function output.

```{r}
test_llr(mods_recs[[1]], mods_recs[[3]]) %>% tab_ti()
```

The above three test statistics are related in an additive manner, so models with multiple regressors can be reduced in a step-wise procedure. During every step, partial correlations for regressors can be used as the indication of the next term to be reduced.

```{r, echo=T}
test_llr(mods_recs[[2]], mods_recs[[3]])$stat +
  test_llr(mods_recs[[1]], mods_recs[[2]])$stat -
  test_llr(mods_recs[[1]], mods_recs[[3]])$stat <= 1e-5
```
