---
editor_options:
  chunk_output_type: console
---

## Time Domain TSA

- [Prophet](https://facebook.github.io/prophet/)
  * Prophet is a procedure for forecasting time series data based on an additive model where non-linear trends are fit with yearly, weekly, and daily seasonality, plus holiday effects. It works best with time series that have strong seasonal effects and several seasons of historical data.
  * Prophet is robust to missing data and shifts in the trend, and typically handles outliers well.
- [Forecasting: Principles and Practice, V3](https://otexts.com/fpp3/)
- Machine Learning with R, the tidyverse, and mlr
- [Some R Time Series Issues, TSA2](https://www.stat.pitt.edu/stoffer/tsa2/Rissues.htm)

### `tsibbles`, `feasts`, `fable`

- [Time series graphics using feasts](https://robjhyndman.com/hyndsight/feasts/)
- [Tidy time series data using tsibbles](https://robjhyndman.com/hyndsight/tsibbles/)
- [Electricity demand data in tsibble format](https://robjhyndman.com/hyndsight/electrictsibbles/)
- [Reintroducing tsibble: data tools that melt the clock](https://blog.earo.me/2018/12/20/reintro-tsibble/#tsibble-key-index)

The fable ARIMA() function uses an alternate parameterisation of constants to stats::arima() and forecast::Arima(). While the parameterisations are equivalent, the coefficients for the constant/mean will differ.

In fable, the parameterisation used is:

$$ (1-φ_1B - \cdots - φ_p B^p)(1-B)^d y_t = c + (1 + θ_1 B + \cdots + θ_q B^q)\varepsilon_t $$

In stats and forecast, an ARIMA model is parameterised as:

$$ (1-φ_1B - \cdots - φ_p B^p)(y_t' - μ) = (1 + θ_1 B + \cdots + θ_q B^q)\varepsilon_t $$

where μ is the mean of $(1-B)^d y_t$ and $c = μ(1-φ_1 - \cdots - φ_p)$.


### Interpretation


### Autoregressions (AR) {#AR}

For example \@ref(exm:Fulton), it can be visualised:

```{r}
tsi_fulton %>% ggplot() + geom_line(aes(t, p.log))
```

When using other functions in `feasts`, the univaraite time series must be specified.

```{r, echo=T}
tsi_fulton %>% feasts::gg_tsdisplay(p.log)
```

```{r, echo=T}
tsi_fulton %>% ACF(p.log) %>% autoplot()
```

#### Models

```{r, echo=T}
mods_fulton[[1]] %>% glance() %>% tab_ti()
```

```{r, echo=T}
mods_fulton[[1]] %>% tidy() %>% tab_ti()
```

```{r}
tsi_fulton %>%
  mutate(fit = fitted(mods_fulton[[1]])$.fitted) %>%
  gather(fit, p.log, key = "key", value = "price") %>%
  ggplot() +
    geom_line(aes(t, price, color = key))
```

The model residuals can be analysed using function `gg_tsresiduals()`.

```{r}
mods_fulton[[1]] %>% gg_tsresiduals()
```

and function `qqPlot()`.

```{r}
mods_fulton[[1]] %>% residuals() %>% {.$.resid} %>% qqPlot()
```

### Inference

#### Log Likelihood Ratio Test {-}

```{R}
test_llr_tsi(mods_fulton[[1]], mods_fulton[[2]]) %>% tab_ti()
```

### Mis-Specification Analysis (MSA)

```{r, echo=T}
mods_fulton[[1]] %>% test_jb_tsi() %>% tab_ti()
```

```{r, echo=T}
mods_fulton[[1]] %>%
  residuals() %>%
  features(.resid, ljung_box) %>%
  tab_ti()
```
