---
editor_options:
  chunk_output_type: console
---

## Non-Business-Day Gaps

### Different Functions for Autoregressive Models 

```{r, message=F, echo=T, collapse=T}
mods_fulton_test <- list()

mods_fulton_test[[1]] <- tsi_fulton %>%
  {.$p.log} %>%
  ar.ols(aic = FALSE, order.max = 1, demean = F, intercept = T)

mods_fulton_test[[2]] <- tsi_fulton %>%
  {.$p.log} %>%
  ar.mle(aic = FALSE, order.max = 1, demean = T, intercept = F)
  # There is no way for `ar.mle` to estimate the intercept directly.

mods_fulton_test[[3]] <- tsi_fulton %>%
  {.$p.log} %>%
  arima(order = c(1, 0, 0), include.mean = T, method = "ML")
  # There is no way for `arima` to estimate the intercept directly.

mods_fulton_test[[4]] <- tsi_fulton %>%
  {.$p.log} %>%
  gets::arx(mc = T, ar = 1, mxreg = NULL, qstat.options = c(1,1))

mods_fulton_test[[5]] <- tsi_fulton %>%
  model(fable::ARIMA(p.log ~ 1 + pdq(1, 0, 0)))

mods_fulton_test[[6]] <- tsi_fulton %>%
  {.$p.log} %>%
  arima(order = c(1, 0, 0), include.mean = T, method = "CSS")
```

```{r}
tibble(
  hwi_mods = 1:6,
  intercept = c(
    mods_fulton_test[[1]]$x.intercept, 
    as.double(mods_fulton_test[[2]]$x.mean) * (1 - as.double(mods_fulton_test[[2]]$ar)), 
    as.double(mods_fulton_test[[3]]$coef[2] * (1 - mods_fulton_test[[3]]$coef[1])), 
    mods_fulton_test[[4]]$coefficients[1], 
    as.double(coef(mods_fulton_test[[5]])[2, 3]), 
    as.double(mods_fulton_test[[6]]$coef[2] * (1 - mods_fulton_test[[6]]$coef[1]))
    ), 
  ar1 = c(
    mods_fulton_test[[1]]$ar[1], 
    as.double(mods_fulton_test[[2]]$ar), 
    as.double(mods_fulton_test[[3]]$coef[1]), 
    mods_fulton_test[[4]]$coefficients[2], 
    as.double(coef(mods_fulton_test[[5]])[1, 3]), 
    as.double(mods_fulton_test[[6]]$coef[1])
    )
  ) %>%
  tab_ti()
```

### Fill Non-Business-Day Gaps with `NA`

```{r, warning=F, message=F, echo=T}
tsi_fulton_t <- read_csv("~/GitHub/TidySimStat/data/Fulton.csv") %>%
  # mutate(p = exp(LogPrice)) %>% 
  mutate(t = ymd(Date)) %>%
  mutate(p.log = LogPrice) %>%
  mutate(i = row_number()) %>%
  select(t, i, p.log) %>%
  as_tsibble(index = t)
```

When `t` is used as the index of `tsibble`, non-business-day (NBD) gaps will be detected. `fill_gaps()` can be used to fill `NA` values for NBD. See [Handle implicit missingness with tsibble](https://tsibble.tidyverts.org/articles/implicit-na.html) for details.

```{r}
tsi_fulton_t %>% fill_gaps() %>% head(14) %>% tab_ti()
```

If `fill_gaps()` is not used, when `fable::ARIMA` is applied, there will be an error stating that the data contains implicit gaps in time. You should check your data and convert implicit gaps into explicit missing values.

```{r}
mods_fulton_test[[7]] <- tsi_fulton_t %>%
  fill_gaps() %>%
  model(fable::ARIMA(p.log ~ 1 + pdq(1, 0, 0)))

mods_fulton_test[[7]] %>% tidy() %>% tab_ti()
```

However, because the existence of `NA` values, the above result turns out to be different from what we obtained in section 1.

```{r}
mods_fulton_test[[5]] %>% tidy() %>% tab_ti()
```

Whether to fill the NBD gaps depends on the context. [Forecasting time series with data on weekdays only, CrossValidated](https://stats.stackexchange.com/questions/327343/forecasting-time-series-with-data-on-weekdays-only). More advanced calendars may be used. [Calendarise self-defined date-times (e.g. business days and time) and respect structural missingness](https://github.com/tidyverts/tsibble/issues/18).

### How to Visualize without NBD Gaps Filled

So if we don't want to fill NBD gaps, a nex index must be added like that in section 1. It is hard to use `autoplot()` with `t` specified as x axis. `ggplot()` must be used.

