---
title: "Linear Regression Analysis of Electricity Consumption"
author: "Edward J. Xu (<edxu96@outlook.com>)"
date: "`r Sys.Date()`"
documentclass: article
classoption: a4paper
output:
  bookdown::html_document2:
    code_folding: hide
    df_print: paged
    fig_caption: no
    fig_height: 7.5
    fig_width: 15
    smooth_scroll: yes
    theme: default
    toc: yes
    toc_float: no
  # tufte::tufte_handout: default
  # tufte::tufte_html: default
editor_options:
  chunk_output_type: inline
---

# Introduction

```{r}
rm(list = ls())
```

Following packages and functions are used in this project.

```{r, message = FALSE, echo=T}
## basic packages
library(knitr)
library(kableExtra)
library(tidyverse)
library(conflicted)
library(magrittr)
library(broom)
## paticular packages for this project
library(lmtest)
library(corrr)
library(tseries)
library(corrplot)
source("../funcs.R")
source("../tests.R")
```

```{r, include=FALSE}
setwd("~/GitHub/TidySimStat/examples/regress")
options(width = 80, pillar.sigfig = 5)
knitr::opts_chunk$set(
  comment = "#>",
  echo = FALSE,
  fig.align="center"
)
```

The data set is defined as follows based on file `recs.csv`:

```{r, message = FALSE, echo=T}
set.seed(6)
dat <-
  read_csv("../../data/recs.csv") %>%
  dplyr::slice(sample(nrow(.), 300)) %>%
  mutate(y = log(KWH / NHSLDMEM)) %>%
  mutate(x8 = TOTROOMS + NCOMBATH + NHAFBATH) %>%
  dplyr::select(y, x2 = NHSLDMEM, x3 = EDUCATION, x4 = MONEYPY, x5 = HHSEX,
    x6 = HHAGE, x7 = ATHOME, x8) %>%
  mutate_at(seq(2, 8), as.integer) %>%  # make continuous variables discrete
  mutate(x5 = - x5 + 2)
```

Different variables are summarized in the following table. `y`, the logarithm of averaged electricity consumption, is the variable that we are interested in. Specifically, The electricity consumption refers to the electricity usage of the house/studio where the respondent lives in 2015, measured in kilowatthours. The quantity is average by the number of household members in the house/studio. That way, it roughly represent the level of electricity consumption of the respondent. Other variables are discussion in the following table.

| Sym | Abbr       | Definition                              |
| --- | ---------- | --------------------------------------- |
| z   | KWH        | electricity consumption                 |
| y   | LKWH.pers  | logarithm of KWH/NHSLDMEM               |
| x2  | NHSLDMEM   | number of household members             |
| x3  | EDUCATION  | highest education completed             |
| x4  | MONEYPY    | annual gross household income last year |
| x5  | HHSEX      | gender                                  |
| x6  | HHAGE      | age                                     |
| x7  | ATHOME     | number of weekdays someone is at home   |
| x8  | TOTROOMS + | number of rooms (including bathrooms)   |

Note that `x8` is a variable indicating the number of rooms of the house/studio of the respondent. It equals the summation of `TOTROOMS`, `NCOMBATH` and `NHAFBATH` in the original data set. `x8` is not included in the initial analysis (sections 1 to 7). 

`x3`, the education level of the respondent, is considered as a continuous variable in this project for simplicity. The detailed definition of different levels is shown in the following table.

| Level | Definition                                  |
| ----- | ------------------------------------------- |
| 1     | Less than high school diploma or GED        |
| 2     | High school diploma or GED                  |
| 3     | Some college or Associate’s degree          |
| 4     | Bachelor’s degree (for example: BA, BS)     |
| 5     | Master’s, Professional, or Doctorate degree |

The first 5 rows of the data set used can be visualized:

```{r}
head(dat, 5) %>% tab_ti(F)
```

In this project, we want to develop a model associating the continuous variable, average electricity consumption, with other variables. We will start by visualizing correlations between variables. In particular, the two variables `x2` and `x6`, which highly correlate with `y` will be explored. The model regressing `y` on `x2` will be discussed in section 2. Four assumptions will be made, three of which will be tested in section 3-5 by Jarque-Bera test (normality), White’s test (homoskedasticity) and RESET test (functional form) respectively. According the test results and discussion in section 6, data point `36` is excluded. Then, in section 7, more regressors are introduced and three new models are established. The detail regarding how regressors interact with each other, namely causality, is discussed in section 8. Based on the understanding of the underlying mechanism, a nonlinear term and `x8` are included as new regressors. Two new models are estimated, based on the only model passing all tests in section 7. Finally, the model called `mods[[7]]` is chosen as the final for presentation and it is interpreted in section 10.

```{r child = './sections/1.Rmd'}
```
